---
title: "Relational Data (joins) Practice"
author: "Turner, BADM 372"
date: "4/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
library(dplyr)
library(nycflights13)
data(flights)
```


Data sets in package ‘nycflights13’:

- airlines  -                       Airline names.
- airports   -                      Airport metadata
- flights    -                      Flights data
- planes      -                     Plane metadata.
- weather     -                     Hourly weather data

## Excercises

1. Remove all flights `flights` from with a missing tail number, and organize the data in descending order for most flights by tail number.  Then add the details about the plane type from `planes`.  You should get something like this:
```{r, echo=FALSE, message=FALSE, out.width="50%"}
q1 <- flights %>% 
  select(tailnum) %>% 
  filter(!is.na(tailnum)) %>% 
  group_by(tailnum) %>% 
  tally() %>% 
  arrange(desc(n)) 
q1 <-   left_join(q1, planes)
head(q1)
```

2. Show the flight details AND weather details for the flight with the longest departure delay.  Remove flights with missing departure delays.  You should get something like this:

```{r, echo=FALSE, message=FALSE, out.width="50%"}
q2 <- flights %>% 
  filter(!is.na(dep_delay)) %>% 
  select(tailnum, dep_delay, year, month, day, hour, origin) %>% 
  mutate(max.delay = max(dep_delay)) %>% 
  filter(dep_delay==max.delay)
q2 <- left_join(q2, weather) %>% 
  select(tailnum, dep_delay, temp, dewp, humid, precip, wind_speed, wind_dir)
q2
```

3. What does it mean for a flight to have a missing tailnum? What do the tail numbers that don’t have a matching record in planes have in common? (Hint: one variable explains ~90% of the problems.)

4. Filter flights to only show flights with planes that have flown at least 100 flights.  How many planes meet this criteria? You should get something like `1,217`.

```{r, echo=FALSE, message=FALSE}
q4 <- flights %>%
  select(tailnum) %>% 
  filter(!is.na(tailnum)) %>%
  group_by(tailnum) %>%
  mutate(n = n()) %>%
  filter(n >= 100) %>% 
  group_by(tailnum) %>% 
  count(tailnum)
```

5. Create as a class a cool, pretty hard question that uses multiple joins.  Write the question.  Answer it.  Like it.  Love it.  Share it with me.  Make sure you feel GREAT about relational data.